\documentclass[11pt]{resume}

\begin{document}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %introduction, contact info and elevator pitch
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \noindent\begin{minipage}[t]{0.73\textwidth}
        \vspace{-5mm}
        {\par \Huge Johnny Pribyl}
        {\par \Large \textcolor{blue}{Senior Software Engineer}}
    \end{minipage}
    \begin{minipage}[t]{0.25\textwidth}
        \setstretch{1.2}
        \vspace{-5mm}
        \begin{flushright}
            {\par \textcolor{black}{\href{mailto:pribylsnbits@gmail.com}{pribylsnbits@gmail.com}}}
            {\par 713-569-3056}
            {\par Bozeman, Montana}
        \end{flushright}
    \end{minipage}
    \begin{minipage}[t]{0.03\textwidth}
        \setstretch{1.2}
        \vspace{-5mm}
        \begin{center}
            {\par \faEnvelope[regular]} 
            {\par \faMobile*} 
            {\par \faMapMarker*} 
        \end{center}
        \vspace{.01mm}
    \end{minipage}

    \noindent\begin{minipage}[t]{1\textwidth}
      \makebox[\linewidth]{\rule{\paperwidth}{0.2pt}}
    \end{minipage}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Education + Work Experience
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \vspace{-1em}
    \noindent\begin{minipage}[t]{1\textwidth}
      {\section* {\large{EDUCATION}}}
      Bachelors of Science in {\bf Professional Physics}. Montana State University,
      2018.
      {\bf 3.95 GPA}

      {\section* {\large{WORK EXPERIENCE}}}
      {\bf Emotive}
      \vspace{.25em}
      \begin{addmargin}[.5em]{0em}
        {\bf \textcolor{blue}{Senior Software Engineer}} {\hfill November 2021 - {\bf \textcolor{blue}{Present}}}
        \vspace{-.5em}
        \begin{itemize}
            \setlength\itemsep{-.2em}

            \item {Transitioned from monolith to microservice architecture to
              ensure scalability while {\bf maintaining a cyclomatic complexity
              of 5 or lower.} This made it possible for teams to function more independently
              and increased the org's velocity}
            \item {Refactored systems to {\bf reduce query times by
              99.9\%} by introducing covering indices and lateral joins into
              our PostgreSQL database. This allowed the database to be downsized which
              lowered operational costs.}
            \item {{\bf Lead the company's "Frontend Guild"} to educate and
              elevate the organization's frontend engineers. We explored topics
              like the transition to React 18, when to use various state
              management solutions, as well as a general best practice consensus.}
            \item {Rewrote legacy React components to {\bf remove unnecessary global
              state} + abstractions allowing for a {\bf ~75\% reduction in total
              lines of code} for a microfrontend}

        \end{itemize}

      \end{addmargin}

      \vspace{-1em}
      \textcolor{gray}{\rule{\textwidth}{0.1pt}}
      \vskip .5em
      \vspace{-.25em}
      {\bf 15Five Inc}
      \vspace{.25em}
      \begin{addmargin}[.5em]{0em}
        {\bf {Engineering Manager}} {\hfill March 2021 - {Oct 2021}}
        \vspace{-.5em}
        \begin{itemize}
            \setlength\itemsep{-.2em}
            \item {Led a team of 4 engineers tasked with maintaining and {\bf
                  improving the core 15Five Check-in feature} of our app.}
            \item {Cultivated a healthy atmosphere by encouraging direct
                  reports to bring their full selves to work through regular
                  1-on-1's, performance reviews, and role clarity discussions
                  which led to {\bf 100\% retention of the engineers on my team}.}
            \item {{\bf Collaborated with designers, product managers, mobile
                  engineers, and other teams} while participating in customer calls
                  to incorporate feedback, build new features, and integrate other
                  teams' work into the Check-in.}
        \end{itemize}

        {\bf {Technical Lead}} {\hfill Oct 2020 - {Oct 2021}}
        \vspace{-.5em}
        \begin{itemize}
            \setlength\itemsep{-.2em}
            \item {{\bf Developed end to end solutions} for all feature work. We
                  typically began by establishing scope before writing and
                  presenting an implementation plan and tickets. During the
                  development cycle I would {\bf write code and review
                  100\% of the relevant pull requests}.}

            \item {Implemented TypeScript adoption at an org level. I
              worked with several other developers to {\bf enforce static
              typing on 100\% of our React components}. This was part of the
              effort that allowed our DevOps team to embrace CI/CD and {\bf
              decrease cycle time by 50\% org-wide}.}

            \item {Architected and built an extensible framework to simplify
                  app-wide rich text editing. I began by investigating existing
                  usage in order to determine the proper abstractions before 
                  {\bf removing 1000s of lines of duplicated code and
                  several abstraction layers} from our codebase.}

        \end{itemize}

        {\bf Frontend Engineer} {\hfill Oct 2019 - Oct 2020}
        \vspace{-.5em}
        \begin{itemize}
            \setlength\itemsep{-.2em}
            \item {Built OKR tracking feature into existing app infrastructure.
                  This feature has {\bf grown into our most adopted feature}. In
                  order to implement this, we had to {\bf integrate custom React hooks
                  and functional components into legacy jQuery} business logic.}
        \end{itemize}
      \end{addmargin}

      \vspace{-1em}
      \textcolor{gray}{\rule{\textwidth}{0.1pt}}
      \vskip .5em

      {\bf LIGO Scientific Collaboration\textemdash \hspace{.5em} Researcher} {\hfill 2013, 2016 - 2018}
      \vspace{.5em}
      \begin{addmargin}[.5em]{0em}
        \begin{itemize}
          \setlength\itemsep{-.2em}

          \item {Wrote applications + received grant funding to develop deep
            neural networks and {\bf model neutron stars} to test Einstein’s
            theory of gravity.}

        \end{itemize}
      \end{addmargin}

      \rule{\textwidth}{0.1pt}

      \vspace{-2em}
      {\section* {\large{OTHER PROJECTS, EXPERIENCE \& SKILLS}}}
      {\bf Skills}
      \vspace{.5em}
      \begin{addmargin}[.5em]{0em}
        \begin{itemize}
          \setlength\itemsep{-.2em}

          \item {Used daily at present\textemdash Docker, JavaScript, TypeScript, React
            (with concurrency!), Python, Django, Git, Arch Linux,
            Sass, Vim, PostgreSQL, CouchDB}

          \item {Used daily in the past\textemdash AWS, AdonisJs, Bash, Bokeh,
              D3, Docker, Express.js, FCM, Hapijs, Heroku, Jupyter, Keras,
              Kubernetes, MariaDB, Mathematica, Matplotlib, NLTK, Node.js,
              Numpy, Pandas, Redis, Redux, RethinkDB, SKLearn, SQLite, SciPy, Seaborn,
              Selenium, Tensorflow}
        \end{itemize}
      \end{addmargin}

      \vspace{.5em}

      {\bf Open source contributions\textemdash \hspace{.5em}} \textcolor{lavender}{\faGithub\hspace{.5em}\underline{\href{http://www.github.com/jpribyl}{github.com/jpribyl}}} \hspace{.5em} \& \hspace{.5em} \textcolor{lavender}{\faGlobe\hspace{.5em}\underline{\href{http://www.johnpribyl.com}{johnpribyl.com}}}
      \vspace{.5em}
      \begin{addmargin}[.5em]{0em}
        \begin{itemize}
          \setlength\itemsep{-.2em}
          \item {Wrote, published, and maintain \verb|react-hook-dragula| and
              \verb|react-hook-mathjax| which have received around 20 stars and
              300 downloads per week. I have also {\bf contributed to React,
              Django}, \verb|vim-test|, and \verb|Freqtrade|.}

          \item {Forked, fixed a deprecation warning, and released
            \verb|action-docker-layer-caching| when unable to reach the
            original maintainer.}

        \end{itemize}
      \end{addmargin}

      \vspace{.5em}
      {\bf Teaching \& Coaching}
      \vspace{.5em}
      \begin{addmargin}[.5em]{0em}
        \begin{itemize}
          \setlength\itemsep{-.2em}
          \item {A combined 8 years of experience coaching soccer and
                tutoring math and physics up to a college level and have worked with ages
              ranging from 5 to 50 years and {\bf subjects ranging from arithmetic to quantum mechanics}.}
        \end{itemize}
      \end{addmargin}

      \vspace{.5em}
      {\bf Grand Canyon Rafting}
      \vspace{.5em}
      \begin{addmargin}[.5em]{0em}
        \begin{itemize}
          \setlength\itemsep{-.2em}

        \item {Successfully led a 3 week, unguided raft trip down 280 river
          miles through the canyon. I planned all the logistics for 16 people.}


        \end{itemize}
      \end{addmargin}
    \end{minipage}
\end{document}
